Printer ballistics through texture analysis of characters

### 2013-11-29 Printer_Ballistics.tex
Artigo finalizado

@@

@@

We would like to thank Professor Anderson Rocha for providing us with the opportunity to meet and learn about a so interesting subject and his student Giuliano Pinheiro, who provided the dataset of scanned documents, without which this work could not be done.

>>>>

Another direction can also be made using other texture analyzers, such as HOG (Histograms of Oriented Gradients Extract) or LBP (Local Binary Patterns), and no GLCM.

@@

Although not the purpose of this study, and future studies, manual extraction of characters is still a counterproductive way of working. Develop a (semi) automated method would be of great benefit to researchers in this field.

@@

We would like to thank Professor Anderson Rocha for providing us with the opportunity to meet and learn about a so interesting subject and his student, Giuliano Pinheiro, who provided the dataset of scanned documents, without which this work could not be done.
